
---
title: "Krill Respirometry Statistics - Summer 2019 Krill"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: cerulean
    highlight: haddock
    smart: false
editor_options: 
  chunk_output_type: inline
---


Hello World

Author: OA Lab, NWFSC
Title: Krill Respirometry Statistics - Summer 2019 Krill
Date: February 2021 (R notebook document)


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(dbplyr)
library(dplyr)
library(purrr)
library(wql)
library(lubridate)
library(tibbletime)
library(arsenal)
library(compareDF)
#for graphing
library(ggplot2)
library(ggfortify)
library(stringr)
library(nlme)
library(RColorBrewer)
library(patchwork)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
library(lme4)
library(lmerTest)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```




 
# 1.) Setting Working Directory
```{r 1.) Setting Working Directory }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_KRLrespirometrySLOPES_STATs")
```



# 2.) DF Creation
```{r 2.) Creating the Dataframe }

#*********************************
## 2.) Creating the intial Dataframe, dRESP
#*********************************
# 46 Vials Magic Number

# 80% threshold
ksSlopes.80 <- read.csv(file = "2021.02.09_ksSlopes.80.csv", stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# 70% threshold
ksSlopes.70 <- read.csv(file = "2021.02.09_ksSlopes.70.csv", stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# 1hr threshold
ksSlopes.1hr  <- read.csv(file = "2021.02.09_ksSlopes.1hr.csv", stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# all points
dSlopes <- read.csv(file = "2021.02.09_Slopes_allpts.csv", stringsAsFactors = FALSE)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```





# 3.) Summary Statisitics on the Unfiltered Dataframe dSlopes
```{r 3 Summary Statisitics on the Unfiltered Dataframe dSlopes}

# factor(dSlopes$TrialID)
# 
# dSlopes <- filter(dSlopes, Treatment != "AMB")  
# dSlopes<- droplevels(filter(dSlopes, Treatment != "AMB"))
#ksSlopes.1hr<- droplevels(filter(ksSlopes1hr, Treatment != "n/a"))

ksSlopes1hr.summary <- ksSlopes.1hr %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(CorrSlope, na.rm = TRUE), 
            mean = mean(CorrSlope, na.rm = TRUE), 
            median = median(CorrSlope, na.rm = TRUE),
            IQR = IQR(CorrSlope, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
ksSlopes1hr.summary

SlopeTable.1hr <- kable(ksSlopes1hr.summary, digits = 4)

write.csv(ksSlopes1hr.summary, "2021.02.09_ksSlopes.1hr_summary.csv")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

ksSlopes80.summary <- ksSlopes.80 %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(CorrSlope, na.rm = TRUE), 
            mean = mean(CorrSlope, na.rm = TRUE), 
            median = median(CorrSlope, na.rm = TRUE),
            IQR = IQR(CorrSlope, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
ksSlopes80.summary

SlopeTable.80 <- kable(ksSlopes80.summary, digits = 4)

write.csv(ksSlopes80.summary, "2021.02.09_ksSlopes.80_summary.csv")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

ksSlopes70.summary <- ksSlopes.70 %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(CorrSlope, na.rm = TRUE), 
            mean = mean(CorrSlope, na.rm = TRUE), 
            median = median(CorrSlope, na.rm = TRUE),
            IQR = IQR(CorrSlope, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
ksSlopes70.summary

SlopeTable.70 <- kable(ksSlopes70.summary, digits = 4)

write.csv(ksSlopes70.summary, "2021.02.09_ksSlopes.70_summary.csv")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dSlopes.summary <- dSlopes %>% group_by(Treatment) %>%
  dplyr::summarize(sd = sd(CorrSlope, na.rm = TRUE), 
            mean = mean(CorrSlope, na.rm = TRUE), 
            median = median(CorrSlope, na.rm = TRUE),
            IQR = IQR(CorrSlope, na.rm = TRUE),
            n = n()) %>%
  mutate(se = sd/sqrt(n)) %>%
  mutate(ci = se*1.96)
dSlopes.summary

SlopeTable.allpts <- kable(dSlopes.summary, digits = 4)

write.csv(dSlopes.summary, "2021.02.09_dSlopes_summary.csv")

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |




```

### 3.a Slope Tables 1hr
```{r 3.a Slope Tables 1hr SlopeTable.1hr }
SlopeTable.1hr <- kable(ksSlopes1hr.summary, digits = 4)
SlopeTable.1hr
```



### 3.b Slope Tables 80%
```{r 3.b SlopeTable.80}
SlopeTable.80 <- kable(ksSlopes80.summary, digits = 4)
SlopeTable.80
```



### 3.c Slope Tables 70%
```{r S3.c Slope Tables SlopeTable.70 }
SlopeTable.70 <- kable(ksSlopes70.summary, digits = 4)
SlopeTable.70
```



### 3.d Slope Tables all points
```{r 3.d dSlopes Table }
dSlopeTable <- kable(dSlopes.summary, digits = 4)
dSlopeTable
```








# 4.) Summary Plots

## 4.a 80% Threshold Corrected Slopes 
```{r }

plot80 <- ggplot(ksSlopes.80, aes(Treatment, CorrSlope)) +
            geom_jitter(color = "grey") +
            geom_jitter(data = ksSlopes.80, aes(Treatment, CorrSlope)) +
            # geom_jitter(data = krillslopes80.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = krillslopes70.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = T1to4krillslopes.filtered, aes(Treatment, slope)) +
            # geom_jitter(aes(colour = Treatment)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = ksSlopes80.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = ksSlopes80.summary, 
                          aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = ksSlopes80.summary,
                          aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("ksSlopes80, (80% oxygen) Corrected Slope") +
            theme_bw() 


plot80
```


The purple dots represent the mean- all trials included
Confidence Intervals set to 95
Green boxplots show from the 25th percentil to the 75th percentile
error bars +/- SD shown in blue
error bars(CI) +/- our confidence intervals- shown in red



## 4.b Plots 70% Slope for Corrected Slopes
```{r }

plot70 <- ggplot(ksSlopes.70, aes(Treatment, CorrSlope)) +
            geom_jitter(color = "grey") +
            geom_jitter(data = ksSlopes.70, aes(Treatment, CorrSlope)) +
            # geom_jitter(data = krillslopes80.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = krillslopes70.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = T1to4krillslopes.filtered, aes(Treatment, slope)) +
            # geom_jitter(aes(colour = Treatment)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = ksSlopes70.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = ksSlopes70.summary, 
                          aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = ksSlopes70.summary,
                          aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("ksSlopes70, (70% oxygen) Corrected Slope") +
            theme_bw() 

plot70

```

The purple dots represent the mean- all trials included
Confidence Intervals set to 95
Green boxplots show from the 25th percentil to the 75th percentile
error bars +/- SD shown in blue
error bars(CI) +/- our confidence intervals- shown in red




## 4.c Plots threshold (1hr) Slope for Corrected Slopes
```{r 4.c Plots 1hr threshold Slope for Corrected Slopes}

Onehrplot <- ggplot(ksSlopes.1hr, aes(Treatment, CorrSlope)) +
            geom_jitter(color = "grey") +
            geom_jitter(data = ksSlopes.1hr, aes(Treatment, CorrSlope)) +
            # geom_jitter(data = krillslopes80.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = krillslopes70.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = T1to4krillslopes.filtered, aes(Treatment, slope)) +
            # geom_jitter(aes(colour = Treatment)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = ksSlopes1hr.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = ksSlopes1hr.summary, 
                          aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = ksSlopes1hr.summary,
                          aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("ksSlopes1hr, (1hr cutoff) Corrected Slope") +
            theme_bw() 

Onehrplot 

```

The purple dots represent the mean- all trials included
Confidence Intervals set to 95
Green boxplots show from the 25th percentil to the 75th percentile
error bars +/- SD shown in blue
error bars(CI) +/- our confidence intervals- shown in red


## 4.c Plots 1hr threshold Slope for Corrected Slopes
```{r Plots 1hr threshold Slope for Corrected Slopes}

dSlopesPlot <- ggplot(dSlopes, aes(Treatment, CorrSlope)) +
            geom_jitter(color = "grey") +
            geom_jitter(data = dSlopes, aes(Treatment, CorrSlope)) +
            # geom_jitter(data = krillslopes80.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = krillslopes70.filtered, aes(Treatment, slope)) +
            # geom_jitter(data = T1to4krillslopes.filtered, aes(Treatment, slope)) +
            # geom_jitter(aes(colour = Treatment)) +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = dSlopes.summary, aes(x=Treatment, y=mean), size=5, color = "purple") + 
            geom_errorbar(data = dSlopes.summary, 
                          aes(x=Treatment, y=mean, ymin = mean-sd, ymax = mean+sd), 
                          color = "blue") +
            geom_errorbar(data = dSlopes.summary,
                          aes(x=Treatment, y=mean, ymin = mean-ci, ymax = mean+ci),
                          colour = "red") +
            # facet_wrap(~TrialID) +
            ggtitle("dSlopes, (all points) Corrected Slope") +
            theme_bw() 
dSlopesPlot

```






# 5.) Descriptive Statisitics 
```{r 25.) Descriptive Statisitics}
library(tidyr)
#Remove NAs
#krill <- na.omit(krill)
#Calculate mean and standard deviation for each treatment per each dataset
# blanks are to be removed from treatments

# dSlopes<- droplevels(filter(dSlopes, Treatment != "n/a"))
# ksSlopes80<- droplevels(filter(ksSlopes80, Treatment != "n/a"))
# ksSlopes70<- droplevels(filter(ksSlopes70, Treatment != "n/a"))
# ksSlopes1hr<- droplevels(filter(ksSlopes1hr, Treatment != "n/a"))


dSlopes_Avg <- tapply(dSlopes$CorrSlope, (dSlopes$Treatment), mean)
dSlopes_Med <- tapply(dSlopes$CorrSlope, (dSlopes$Treatment), median)
dSlopes_Std <- tapply(dSlopes$CorrSlope, (dSlopes$Treatment), sd)

ksSlopes.80_Avg <- tapply(ksSlopes.80$CorrSlope, (ksSlopes.80$Treatment), mean)
ksSlopes.80_Med <- tapply(ksSlopes.80$CorrSlope, (ksSlopes.80$Treatment), median)
ksSlopes.80_Std <- tapply(ksSlopes.80$CorrSlope, (ksSlopes.80$Treatment), sd)

ksSlopes.70_Avg <- tapply(ksSlopes.70$CorrSlope, (ksSlopes.70$Treatment), mean)
ksSlopes.70_Med <- tapply(ksSlopes.70$CorrSlope, (ksSlopes.70$Treatment), median)
ksSlopes.70_Std <- tapply(ksSlopes.70$CorrSlope, (ksSlopes.70$Treatment), sd)

ksSlopes.1hr_Avg <- tapply(ksSlopes.1hr$CorrSlope, (ksSlopes.1hr$Treatment), mean)
ksSlopes.1hr_Med <- tapply(ksSlopes.1hr$CorrSlope, (ksSlopes.1hr$Treatment), median)
ksSlopes.1hr_Std <- tapply(ksSlopes.1hr$CorrSlope, (ksSlopes.1hr$Treatment), sd)


#Put it all together
Slope_Stats <- cbind(dSlopes_Avg, dSlopes_Med, dSlopes_Std,
                     ksSlopes.80_Avg, ksSlopes.80_Med, ksSlopes.80_Std,
                     ksSlopes.70_Avg, ksSlopes.70_Med, ksSlopes.70_Std,
                     ksSlopes.1hr_Avg, ksSlopes.1hr_Med, ksSlopes.1hr_Std)

colnames(Slope_Stats) [1:12] <-c("Avg All Points Corrected Slopes", "Med All Points Corrected Slopes", "All Points Corrected Slopes SD", "Avg 80% DO Corrected Slopes", "Med 80% DO Corrected Slopes", "80% DO Corrected Slopes SD", "Avg 70% DO Corrected Slopes", "Med 70% DO Corrected Slopes", "70% DO Corrected Slopes SD", "Avg 1hr Corrected Slopes", "Med 1hr Corrected Slopes", "1hr Corrected Slopes SD")


write.csv(Slope_Stats, "2021.02.09_Slope_Stats.csv")

kable(Slope_Stats)

```




# 6.) Fitting my Linear Mixed-Effects Models to my Dataframes 
```{r Repeated measures analysis}
#Using a mixed model to find significant differences bertween MOATs
#library(nlme)
library(lme4)
library(lmerTest)

# Corrected Slopes , Treatment taking into account MOATS


# ksSlopes.80<- droplevels(filter(ksSlopes.80, Treatment != "n/a"))
# ksSlopes.70<- droplevels(filter(ksSlopes.70, Treatment != "n/a"))
# ksSlopes.1hr<- droplevels(filter(ksSlopes.1hr, Treatment != "n/a"))
# dSlopes<- droplevels(filter(dSlopes, Treatment != "n/a"))


ksSlopes.1hr_howmanyanimalsin_CHG <- subset(ksSlopes.1hr, Treatment == "CHG")
ks1hrCHGno <- unique(ksSlopes.1hr_howmanyanimalsin_CHG$KrillID)
# 16 animals in All Change across 4 trials

ksSlopes.1hr_howmanyanimalsin_CUR <- subset(ksSlopes.1hr, Treatment == "CUR")
ks1hrCURno <- unique(ksSlopes.1hr_howmanyanimalsin_CUR$KrillID)
# 19 animals from Current Treatment across 4 trials

ksSlopes.1hr_howmanyanimalsin_TMP <- subset(ksSlopes.1hr, Treatment == "TMP")
ks1hrTMPno <- unique(ksSlopes.1hr_howmanyanimalsin_TMP$KrillID)
# 16 animals in high Temperature Treatment across 4 trials


16+19+16
# [1] 51

```


#### 6.a 1hr Dataframe - LMER
```{r, 6.a) 1hr Dataframe - LMER}
lmer.ksSlopes.1hr <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.1hr)
summary(lmer.ksSlopes.1hr)
# All Change Against Current 
# All Change Against High Temperature
```

"1hr Dataset" - No Treatment Effect Found

Random Effects Model variance accounting for a possible MOATs effect remains significantly small.
No treatment effect observed. 
Neither correlation or T values between "All Change(CHG)" to "Current(CUR)" and "High Temperature(TMP)" 
This model doesn't consider High Temperature directly against Current
Model re-ogranized/re-leveled below


#### 6.b 1hr Dataframe - LMER releved Current 1st
```{r 6.b) 1hr threshold Dataframe - LMER}

levels(ksSlopes.1hr$Treatment)
# lmer.ksSlopes.1hr 
ksSlopes.1hr$Treatment <- fct_relevel(ksSlopes.1hr$Treatment, "CUR")
lmer.ksSlopes.1hr <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.1hr)
summary(lmer.ksSlopes.1hr)

```

The Current Conditions to Hight Temperature comparison did not display a treatment effect. 

Possible reasons for such small amount of variance include only 51 animals in trial.
16 animals from the "All Change" treatment were in included across four trials.
19 animals from the "Current" treatment were in included across four trials.
16 animals from the "High Temperarure" treatment were in included across four trials.
(totals 51 animals)

so signal over the noise- why?

1hr may not have allowed enough observations to show a disernable difference across treatments.
However, Krill could just be proving to be a robust organism, able to withstand a cross stress environment. 
It's more likely that sample size was small.



#### 6.c 80% Threshold Dataframe - LMER
```{r, 6.c) 1hr Dataframe - LMER}
lmer.ksSlopes.80 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.80)
summary(lmer.ksSlopes.80)
# All Change Against Current 
# All Change Against High Temperature
```

The 80% (DO) Threshold t values are slightly smaller. 
The variance around a MOATs effect remains significantly small.
No treatment effect observed.
Model re-organized/re-leveled below to compare "Current" against "High Temperature" directly



#### 6.d 80% Threshold - LMER releved Current 1st
```{r 6.d) 80% Dataframe - LMER}

levels(ksSlopes.80$Treatment)
# lmer.ksSlopes.1hr 
ksSlopes.80$Treatment <- fct_relevel(ksSlopes.80$Treatment, "CUR")
lmer.ksSlopes.80 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.80)
summary(lmer.ksSlopes.80)

```
When comparing Current against "High Temperature" and "All Change" the T values remain small but the TMP to CUR is somewhat larger. 

Still, no discernible treatment effect, no discernible MOATS effect. 



#### 6.e 70% Threshold Dataframe - LMER
```{r, 6.e) 70% Dataframe - LMER}
lmer.ksSlopes.70 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.70)
summary(lmer.ksSlopes.70)
# All Change Against Current 
# All Change Against High Temperature
```


The variance around a MOATs effect remains significantly small in this 70% Threshold dataset.
No treatment effect observed.
Model re-organized/re-leveled below to compare "Current" against "High Temperature" directly


#### 6.f 70% Threshold - LMER releved Current 1st
```{r 26.f) 70% Dataframe - LMER}

levels(ksSlopes.70$Treatment)
# lmer.ksSlopes.1hr 
ksSlopes.70$Treatment <- fct_relevel(ksSlopes.70$Treatment, "CUR")
lmer.ksSlopes.70 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.70)
summary(lmer.ksSlopes.70)

```

No discernible treatment effect, no discernible MOATS effect. 
None of the "threshold confined" datasets displayed a MOATs or Treatment Effect.


Below shows the comparison is slopes values when all data points were considered. 


#### 6.g All Points "dSlopes" Dataframe - LMER
```{r, 6.g) All Points Dataframe - LMER}
lmer.dSlopes<- lmer(CorrSlope ~ Treatment + (1|MOATS), data = dSlopes)
summary(lmer.dSlopes)
# All Change Against Current 
# All Change Against High Temperature
```


The variance around a MOATs effect remains so significantly small.
No MOATs effect
No treatment effect observed.
Model re-organized/re-leveled below to compare "Current" against "High Temperature" directly


#### 6.f) All Points - LMER releved Current 1st
```{r 6.f) All Points - LMER}

levels(dSlopes$Treatment)

dSlopes$Treatment <- fct_relevel(dSlopes$Treatment, "CUR")
lmer.dSlopes <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = dSlopes)
summary(lmer.dSlopes)

```



```{r Models Commented Out & next step thoughts}
# 
# # Just a chunk of the models held back case I need them.  
# 
# lmer.ksSlopes.80 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.80)
# summary(lmer.ksSlopes.80)
# 
# lmer.ksSlopes.70 <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = ksSlopes.70)
# summary(lmer.ksSlopes.70)
# 
# lmer.dSlopes <- lmer(CorrSlope ~ Treatment + (1|MOATS), data = dSlopes)
# summary(lmer.dSlopes)
# 
# 
# 
# # what about different rounds on different days?
```




```{r}

Onehrplot
```


```{r}
plot70
```



```{r}
plot80
```


```{r}
dSlopesPlot
```




*Slope Statistics*
```{r}
kable(Slope_Stats)
```


*Krill Slopes 1hr Summary Table*
```{r}
kable(ksSlopes1hr.summary, digits = 4)
```


*Krill Slopes (70min cutoff) Summary Table*
```{r}
kable(ksSlopes70.summary, digits = 8)
```


*Krill Slopes (80min cutoff) Summary Table*
```{r}
kable(ksSlopes80.summary, digits = 8)
```


*Krill Slopes (all points) Summary Table*
```{r}
kable(dSlopes.summary, digits = 8)
```


*Krill Slopes (1hr cutoff) Mixed Effects Model*
```{r}
summary(lmer.ksSlopes.1hr)
```


*Krill Slopes (80min cutoff) Mixed Effects Model*
```{r}
summary(lmer.ksSlopes.80)
```


*Krill Slopes (70min cutoff) Mixed Effects Model*
```{r}
summary(lmer.ksSlopes.70)
```


*Krill Slopes (all points) Mixed Effects Model*
```{r}
summary(lmer.dSlopes)
```



# 7.) Linear Models All Change Compared Against Current and High Temperature
## 7.a) dSlopes all points 
```{r}

dSlopes$Treatment <- as.character(dSlopes$Treatment)

dSlopeFIT <- lm(CorrSlope ~ Treatment, data=dSlopes)
summary(dSlopeFIT )
```

```{r}
plot(dSlopeFIT)
```



# 7.b) Linear Models All Change Compared Against Current and High Temperature (80%)
```{r}
ksSlopes.80$Treatment <- as.character(ksSlopes.80$Treatment)

ksSlope.80FIT <- lm(CorrSlope ~ Treatment, data=ksSlopes.80)
summary(ksSlope.80FIT)
```

```{r}
plot(ksSlope.80FIT)
```



# 7.c) Linear Models All Change Compared Against Current and High Temperature (70%)
```{r}
ksSlopes.70$Treatment <- as.character(ksSlopes.70$Treatment)

ksSlope.70FIT <- lm(CorrSlope ~ Treatment, data=ksSlopes.70)
summary(ksSlope.70FIT)
```

```{r}
plot(ksSlope.70FIT)
```





# 7.d) Linear Models All Change Compared Against Current and High Temperature (1hr)
```{r}
ksSlopes.1hr$Treatment <- as.character(ksSlopes.1hr$Treatment)

ksSlope.1hrFIT <- lm(CorrSlope ~ Treatment, data=ksSlopes.1hr)
summary(ksSlope.1hrFIT)
```

```{r}
plot(ksSlope.1hrFIT)
```
Noticing that the 1hr dataset doesn't fit the model well- going to further explore the model. 
Maybe this just calls a difference between Trial 03 and all others



# Question Times 1hr Dataset 
When I write the following expression does this mean that I'm looking at the relationship of (CorrSlope ~ Treatment) of each MOATs?
```{r}
ksSlope.1hr.MOATsFIT <- lm(CorrSlope ~ Treatment + MOATS, data=ksSlopes.1hr)
summary(ksSlope.1hr.MOATsFIT)
```

# Want to also account for Trial ID

```{r}
ksSlope.1hr.MOATsTrialIDFIT <- lm(CorrSlope ~ Treatment + MOATS + TrialID, data=ksSlopes.1hr)
summary(ksSlope.1hr.MOATsTrialIDFIT)
```

# Rather than MOATs I'll try Trial ID in my mixed effects model

# 9.x Trial ID
#### 9.a 1hr Dataframe - LMER
```{r, 6.a) 1hr -LMER}
lmer.ksSlopesTrialID.1hr <- lmer(CorrSlope ~ Treatment + (1|TrialID), data = ksSlopes.1hr)
summary(lmer.ksSlopesTrialID.1hr)
# All Change Against Current 
# All Change Against High Temperature
```

"1hr Dataset" -still no Treatment Effect Found



#### 6.b 1hr Dataframe - LMER releved Current 1st
```{r 6.b 1hr Dataframe-LMER}

levels(ksSlopes.1hr$Treatment)
# lmer.ksSlopes.1hr 
ksSlopes.1hr$Treatment <- fct_relevel(ksSlopes.1hr$Treatment, "CUR")
lmer.ksSlopesTrialID.1hr <- lmer(CorrSlope ~ Treatment + (1|TrialID), data = ksSlopes.1hr)
summary(lmer.ksSlopesTrialID.1hr)

```
Trial Variance may not be leading vairiance determinator. 





```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT












